\section*{LIST OF PARTICIPATING ORGANISATIONS}
\note{List of participants.  Max 2 pages}

\begin{msctable}{|>{\ra}p{25mm}|>{\ra}p{25mm}|c|c|>{\ra}p{12mm}|c|>{\ra}p{25mm}|>{\ra}p{20mm}|>{\ra}p{20mm}|}
    \colorrow
    \hline
    \textbf{Consortium member} &
    \textbf{Legal entity short name} &
    \rotatebox[origin=c]{90}{\parbox{17mm}{\textbf{Academic}}} &
    \rotatebox[origin=c]{90}{\parbox{17mm}{\textbf{Non-academic}}} &
    \textbf{Awards doctoral degrees} &
    \rotatebox[origin=c]{90}{\parbox{17mm}{\textbf{Country}}} &
    \textbf{Dept. / Division / laboratory} &
    \textbf{Scientist-in-charge} &
    \textbf{Role of associated partner} \\
    \hline
    \colorrow
    \textbf{Beneficiaries} &&&&&&&& \\
    \hline
    \colorrow
    \textbf{Associated partners} &&&&&&&& \\
    \hline
    \colorrow
    \textbf{Associated partners linked to a beneficiary} &&&&&&&& \\
    \hline
\end{msctable}

\note{Use the same participant numbering and names as in the administrative proposal forms. These are labelled Partners (instead of beneficiary) in Part A.}

%Notes:
%\begin{compactenum}
%\end{compactenum}

\subsubsection*{Data for non-academic beneficiaries:}
% 180 - 9*5 = 135mm
\begin{msctable}{|>{\ra}p{12mm}|>{\ra}p{12mm}|>{\ra}p{12mm}|>{\ra}p{12mm}|>{\ra}p{12mm}|>{\ra}p{39mm}|>{\ra}p{12mm}|>{\ra}p{12mm}|>{\ra}p{12mm}|}
    \colorrow
    \hline
    \textbf{Name} &
    \textbf{Location of research premises} &
    \textbf{Type of R\&D activities} &
    \textbf{No. of full-time employees} &
    \textbf{No. of employees in R\&D} &
    \textbf{Web site} &
    \textbf{Annual turnover} &
    \textbf{Entreprise status} &
    \textbf{SME status} \\
    \hline
\end{msctable}

\note{Information must be based on current data, not projections. Will be verified during the Grant preparation phase.}

\subsubsection*{Declarations:}
\begin{msctable}{|>{\ra}p{48mm}|>{\ra}p{116mm}|}
    \colorrow
    \hline
    \textbf{Name (institution/individual)} &
    \textbf{Nature of interrelationship} \\
    \hline
\end{msctable}

\note{Applicants \textbf{must} use this table to declare any inter-relationship between the participating organisations and individuals (e.g. family-ties, shared premises or facitilites, joint ownership, financial interests, overlapping staff or directors, etc.)}
\newpage
\centerline{Page left blank for consistent page count.}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "master"
%%% TeX-PDF-mode: t
%%% End:
